%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Info
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Louis Pahlavi
% Email:  louis.pahlavi@mail.utoronto.ca

% This is my personal resume. All the document setup is made inside the
% "Resume" template.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% General setup
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{ResumeTemplate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Title and headers
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\name{Louis L. W. D. Pahlavi}
	
	\contact{106 Wineva Ave}{Toronto}{M4E 2T2}{+1-(647)-909-5487}{louis.pahlavi@mail.utoronto.ca}
	%{$\cdot$ }{\href{https://lpahlavi.github.io}{lpahlavi.github.io}}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Education
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{EDUCATION}
	\datedsubsection{University of Toronto}{September 2014--Present}
	\workitemsthree
	{{\textit{Bachelor of Applied Science in Electrical and Computer Engineering}, expected completion May 2019}}
	{Minor in Robotics and Mechatronics}
	{Latest term 92.1\% average (ranked 4 out of 173), 3.86/4.00 cumulative GPA}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Education
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{INDUSTRY EXPERIENCE}
	
	\position{Systems and Control Engineering Intern}{May 2017--August 2018}{\href{https://veritystudios.com/}{Verity Studios AG}}

	\workitemsthree
	{Serviced entertainment drone show systems overseas and oversaw flight operations for several weeks.}
	{Worked on improving the onboard control algorithms of swarms of quadcopters implemented in C++.}
	{Evaluated and characterized flight performance and effectiveness of calibration routines using Python.}
	
	\position{Radio Frequencies Engineer}{June 2015--September 2015}{\href{https://www.utias-sfl.net/}{Space Flight Laboratories}}

	\workitemsone
	{Designed and simulated the early prototypes of a deployable antenna mounted on the NORSAT-2 maritime communications satellite (launched in 2017) in collaboration with the European Space Agency.}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Education
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{RESEARCH EXPERIENCE}
	
	\position{Researcher}{May 2016--August 2016}{\href{http://www.lbb.ethz.ch/}{ETH Z{\"u}rich Laboratory for Biosensors and Bioelectronics (LBB)}}

	\workitemstwo
	{Developed the control and processing software for a biosensor to measure the density of proteins in liquid.}
	{Created a Graphical User Interface using Qt to control the actuators and interface them with various sensors.}
	
	\position{Researcher}{May 2015--June 2015}{University of Toronto Reconfigurable Antenna Laboratory}

	\workitemsone
	{Created a MATLAB simulation to model a satellite's orbit and predict antenna radiation intensity on the surface of the Earth. Worked on antenna synthesis to find an antenna array for a given desired coverage area.}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Projects and Teaching
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{PROJECTS AND TEACHING}
	
	\position{Teaching Assistant}{September 2016--December 2016}{University of Toronto Faculty of Engineering}

	\workitemsone
	{Taught APS100 -- 'Orientation to Engineering' to first year Electrical and Computer Engineering students.}
	
	\position{Wireless Communications Lead}{September 2014--June 2016}{\href{https://www.utat.ca/space-systems/}{University of Toronto Aerospace Team}}

	\workitemstwo
	{Designed, built and tested the antenna and communication module PCB, on a student-built nano satellite.}
	{Presented our design at several Product Design Reviews (PDR) and the Critical Design Review (CDR).}

	% \position{Ground School Instructor}{September 2014--January 2015}{330 Danforth Tech RCACS}
	%
	% \workitemsone
	% {Coordinated and taught the pilot ground school course at 330 Danforth Tech Royal Canadian Air Cadet Squadron.}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Awards and Scholarships
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{SCHOLARSHIPS AND AWARDS}	
	\begin{itemize}[noitemsep, leftmargin=*]
		\item \textbf{Faculty of Applied Science and Engineering Dean's Honours List} \hfill 2014--Present
		\item \textbf{Gordon R. Slemon Scholarship} -- Awarded for engineering design and academic excellence \hfill 2016
		\item \textbf{University of Toronto International Exchange Bursary} \hfill 2016
		\item \textbf{University of Toronto Centre for International Exchange Award} \hfill 2016
		\item \textbf{Royal Canadian Air Cadet Glider and Power Pilot Scholarships} \hfill 2013, 2014\vspace*{-\baselineskip}
	\end{itemize}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% Technical Skills
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{TECHNICAL SKILLS}
	\raggedright
	\begin{itemize}[noitemsep, leftmargin=*]
		\item \textbf{Programming Languages:} Python, C/C++,  MATLAB \\
		\item \textbf{Software and CAD:} Unix, Git, LaTeX, Tensorflow, Qt\\
		\item \textbf{Languages:} French (native),  English (native),  Italian (fluent),  German (intermediate), Czech (basic)\vspace*{-\baselineskip}
	\end{itemize}

\end{document}